Experiences in teaching with Jupyter, Jupyterhub, and nbgrader

### 2019-11-01 paper/paper.tex
project number added to acknowledgments
desc of USl

Back in 2017 the collaboration between three partners University of
Augsburg, European University Cyprus and University of Silesia has
been initiated in the form of Erasmus+ project. The general aim was to
research on possibility of implementing good practices in using Python
programming language and Jupyter notebook in teaching in different
environments. Experience among parters with both Python and Jupyter
were diversified. It opened a possibility to observe a process of an
adotion of new educatioal approach at different phases at the same
time.

@@

\texttt{Description of each partner specifics}

@@

@@

A Jupyter notebook consists of a collection of two types of cells, namely code
cells and text cells. The latter may contain text written in markdown, possibly
including formulas as well as figures. This structure facilitates to guide
students through a problem set. Usually, the code in a notebook is intended to
be executed in a linear fashion even though this is not imposed by the
notebook. In fact, the notebook should invite students to experiment which
implies the opening of new cells and the execution of code written by the
student. In this process, out-of-order execution naturally occurs and can have
side effects which tend to confuse students. While the order of execution of
individual cells can be inferred by the sequence number attributed to a cell
once it has been executed, in particular beginners are not aware of the
problems that out-of-order execution can entail.

@@

\begin{acknowledgements}
This work was supported through the Erasmus+ programme of the
European Union.
\end{acknowledgements}

>>>>

Back in 2017 the collaboration between three partners University of
Augsburg, European University Cyprus and University of Silesia has
been initiated in the form of Erasmus+ project. The general aim was to
research on possibility of implementing good practices in using Python
programming language and Jupyter notebook in teaching in different
environments. Experience among parters with both Python and Jupyter
were diversified. It opened a possibility to observe a process of an
adoption of new educatioal approach at different phases at the same
time.

@@

\subsection{University of Aubgsburg}

@@

\subsection{University of Silesia}

At the University of Silesia Python used to be a a first programming
language for students of Applied Computer Science. There has beem
implemented a concept of ``mobile computer classroom'' which consists
of inexpensive and mobile computers which are are available to
students in the rental office. Initially it consisted of 10-inch
netbooks, currently the hardware is based on Chromebooks which are
very easy to maintain. Therefore an important aspect is the
accessibility of the work environment in a web browser. Jupyter
notebook fits perfectly in such a scenario. In recent years several
work scenarios based on Juyter notebook have been developed in such an
environment.

Here, we will mainly concentrate on the case of course ``Introduction
to Artifitial Intelligence``, which is attented by c.a. 50 students
every year. The course used Jupyter notebook as a teaching tool during
the lectures and tutorials. Students had to submit their work in the
form of notebooks form. Additionally automating testing software has been 
used to help both students as well as teachers.

\subsection{University of Cyprus}

@@

Generally speaking, a Jupyter notebook is a document mixing prose,
code, visualization, together with resources: source code, data,
media.  It consists of a collection of two types of cells, namely code
cells and text cells. The latter may contain text written in markdown,
possibly including formulas as well as figures. This structure
facilitates to guide students through a problem set. Usually, the code
in a notebook is intended to be executed in a linear fashion even
though this is not imposed by the notebook. In fact, the notebook
should invite students to experiment which implies the opening of new
cells and the execution of code written by the student. In this
process, out-of-order execution naturally occurs and can have side
effects which tend to confuse students. While the order of execution
of individual cells can be inferred by the sequence number attributed
to a cell once it has been executed, in particular beginners are not
aware of the problems that out-of-order execution can entail.

@@

\begin{acknowledgements}
This work was supported by the European Union through Erasmus+ project
2017-1-PL01-KA203-038747.
\end{acknowledgements}
